Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-15 analysis/paper/paper.Rmd
clean up description of methods

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package (version `r packageVersion("dplyr")`) [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.

>>>>

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.
